Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker qual keyneed added. +tl;dr added

@@

@@

@@

>>>>

TL;DR: Situational core need relates significantly to outgroup addititudes. The core need has little explained variance between participants (compared to the null model: Variance Explained = 1 – (Var with Predictor/Var without Predictor); `r format(round(v.keyneed.btw.perc, 2),nsmall=2)`%). The variance explained within participants is small to medium (`r format(round(v.keyneed.within.perc, 2),nsmall=2)`%)

@@

TL;DR: The random slope adds significantly to the prediction model.

<div class="alert alert-warning alert-dismissible fade in" role="alert">
  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
  <i class="fas fa-exclamation-triangle"></i> <b>Check needed: </b><br/>
  Something is with the variances explained (between = `r format(round(v.keyneed.ran.btw.perc, 2),nsmall=2)`%, within = `r format(round(v.keyneed.ran.within.perc, 2),nsmall=2)`%). This is when comparing the random intercepts to the random slopes model.
</div>

@@

TL;DR: Situational core need relates significantly to interaction quality. The core need explained substantial variance between participants (`r format(round(v.qual.keyneed.btw.perc, 2),nsmall=2)`%). The variance explained within participants is also medium (`r format(round(v.qual.keyneed.within.perc, 2),nsmall=2)`%)

@@

```{r slopesQualKeyNeed}
# Create and save Model (optimizer needed to reach convergence)
  model.qual.keyneed.ran = lme(quality_overall_1~
                         keymotive_fulfillemt_1, 
                         random=~1+keymotive_fulfillemt_1|PID,
                       control=lmeControl(opt='optim'), data=workerOutgroupInteraction)

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
  summ(model.qual.keyneed.ran0 <- lmer(quality_overall_1 ~
                           keymotive_fulfillemt_1 + 
                           (1+keymotive_fulfillemt_1|PID), 
                         data=workerOutgroupInteraction), 
       confint = TRUE, digits = 3, center = TRUE)

# Compare new model to previous step
  anova(model.qual.keyneed, model.qual.keyneed.ran) %>%
    as.data.frame %>%
    select(-call) %>%
    kbl(., 
        #label = "",
        caption = "Worker: Model Comparison",
        format = "html", 
        linesep = "",
        booktabs = T,
        align = rep('c', ncol(.)),
        digits = 3)  %>%
  kable_styling(position = "left")

# Save variances
  v.qual.keyneed.ran = lme4::VarCorr(model.qual.keyneed.ran)

# The estimate of between-group (or Intercept variance) explained: 
  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
    v.qual.keyneed.ran.btw <- 1 - (as.numeric(v.qual.keyneed.ran[1])/as.numeric(v.qual.keyneed[1]))
    v.qual.keyneed.ran.btw.perc <-  (1 - (as.numeric(v.qual.keyneed.ran[1])/as.numeric(v.qual.keyneed[1])))*100
  # and the estimate of within-group (or residual variancel) explained is:
    v.qual.keyneed.ran.within <- 1 - (as.numeric(v.qual.keyneed.ran[2])/as.numeric(v.qual.keyneed[2]))
    v.qual.keyneed.ran.within.perc <- (1 - (as.numeric(v.qual.keyneed.ran[2])/as.numeric(v.qual.keyneed[2])))*100
```

TL;DR: random slopes does not add significantly. Stay with simpler model.
